\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-10-01 NAR_DRAFT.tex
stab at fixing figure legend

\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wes.pdf}
  \end{center}
  \caption{Performance of various posterior probability thresholds in 500X exomes. 
  For realistic posterior probability thresholds,  positive predictive values are greater for \batcave than MuTect, no matter the concentration of the mutation profile.
  }
\label{NAR-ppv_fig}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
  \includegraphics{figures/ppv_wes.pdf}
  \end{center}
  \caption{Performance of various posterior probability thresholds in 500X exomes. 
  For realistic posterior probability thresholds,  \batcave has a positive predictive value that is better calibrated than MuTect, no matter the concentration of the mutation profile.
  }
\label{NAR-ppv_fig}
\end{figure}
